%-------------------------
% Resume in Latex
% Author : Yash Ramesh Shelar
% Based off of: https://github.com/YashShelar007/resume-yash-shelar
% License : MIT
%------------------------

\documentclass[a4paper, 10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
% \usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\usepackage[bottom=2.1cm, top=2.1cm, left=2.1cm, right=2.1cm]{geometry}
\usepackage{xcolor}
\usepackage[colorlinks = true,linkcolor = blue,
            urlcolor  = blue, citecolor = blue,
            anchorcolor = blue]{hyperref}

\newcommand{\MYhref}[3][blue]{\href{#2}{\color{#1}{#3}}}

\usepackage{newtxtext,newtxmath}
\usepackage{ragged2e}
\setlist{label=\textbullet}
\setlength{\footskip}{3.60004pt} 
\usepackage{anyfontsize}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\setlength{\hsize}{\hsize}


\titleformat{\section}{
  \scshape\bfseries\raggedright
}{}{0em}{\MakeUppercase}[\color{black}\titlerule]


% Ensure that generated pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeEducationContent}[4]{
  \item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{#2} \\ 
      {#3} & {#4} \\
    \end{tabular*}
}
\newcommand{\resumeExperienceHeading}[2]{
    \item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \textbf{#2}
    \end{tabular*}
    \vspace{-15pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{#2}
    \end{tabular*}
    \vspace{-15pt}
}

%-------------------------------------------
%%%%%%%%%%%%%%%%%%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\justifying
\begin{center}
    \textbf{\Large \scshape YASH RAMESH SHELAR} \\
         {623-281-8692} $|$ \href{mailto:yshelar2000@gmail.com}{yshelar2000@gmail.com} $|$ 
    \href{https://www.linkedin.com/in/shelar-yash/}{LinkedIn/shelar-yash} $|$
    \href{https://github.com/YashShelar007}{GitHub/shelar-yash} $|$ 
    \href{https://yashshelar.com/}{Portfolio/shelar-yash} $|$ Tempe, AZ
\end{center}
\vspace{-15pt}
%-----------EDUCATION-----------
\section{Education}
    \vspace{-5pt}
    \begin{itemize}[itemsep=1pt, leftmargin=0in, label={}]
        \resumeEducationContent
          {Master of Science in Computer Science (Thesis)}{July 2025}
          {Arizona State University, Tempe, AZ}{GPA: 3.50}
          \vspace{-10pt}
          \begin{itemize}[itemsep=-1pt]
              \item{\textbf{Thesis}: Model Compression as a Service for Resource-constrained Edge Devices.}
              \item{\textbf{Relevant Coursework}: Cloud Computing, Foundation of Algorithms, Mobile Computing, Data Visualization.}
          \end{itemize}
        \resumeEducationContent
          {Bachelor of Science in Computer Science}{Dec 2022}
          {Arizona State University, Tempe, AZ}{GPA: 3.92}
          \vspace{-10pt}
          \begin{itemize}[itemsep=-1pt]
              \item{\textbf{Honors}: Summa Cum Laude, New American Scholar, Dean’s List.}
              \item{
              \textbf{Relevant Coursework}: Data Structures \& Algorithms, Object-Oriented Programming, Operating Systems, Machine Learning, Artificial Intelligence, Software Engineering, Database Management.}
          \end{itemize}
    \end{itemize}

\vspace{-15pt}
%-----------PROGRAMMING SKILLS-----------
\section{Programming Skills}
    \vspace{-5pt}
    \begin{itemize}[itemsep=-1pt, leftmargin=0in, label={}]
        \item{\textbf{Programming Languages}: Python, C, C++, Go, Java, Javascript, Typescript, SQL, Shell, C\#, .NET.}
        \item{\textbf{Frameworks \& Libraries}: React.js, Node.js, Flask, Spring Boot, Angular, Express.js, REST, gRPC, PyTorch, TensorFlow.}
        \item{\textbf{Cloud \& DevOps}: AWS (Lambda, ECS, S3, API Gateway, DynamoDB, CloudWatch, EKS, SES, SQS, CloudFormation), GCP, Docker, Kubernetes, Terraform, GitHub Actions, Jenkins, CI/CD, NGINX.}
        \item{\textbf{Databases}: PostgreSQL, MySQL, OracleDB, MongoDB, DynamoDB, Cassandra, Redis.}
        \item {\textbf{Tools \& Platforms}: Git, Jira, Apache Kafka, Hadoop, Spark, Sentry, Grafana, Appwrite, Snowflake, Linux/Unix, macOS.}
    \end{itemize}

\vspace{-15pt}
%-----------EXPERIENCE-----------
\section{Experience}
    \vspace{-5pt}
    \begin{itemize}[itemsep=1pt,leftmargin=0in, label={}]
        % Experience #1
        \resumeExperienceHeading{Cloud \& ML Researcher \textbar\ \href{https://visa.lab.asu.edu/}{VISA Research Lab}}{Jan 2024 - Present}
        \begin{itemize}[itemsep=1pt]
            \item Reduced manual compression time by 90\% and deployment failures by 42\% by designing a serverless ML model compression pipeline on AWS that scaled to 1,200+ monthly executions across 12+ model architectures with 99\% success rate.       
            
            \item Improved observability and reduced support tickets by 35\% by building a real-time UI using React/Tailwind, integrating Step Functions and DynamoDB-backed metrics, and cutting inference recovery time by 35\%.
            
            \item Accelerated release cycles by 6× and achieved zero-downtime CI/CD as measured by reducing release time from 30 minutes to under 5 minutes, by automating infrastructure with Terraform and GitHub Actions.
            
            \item \textbf{Tech-stack:} Python, Bash, PyTorch, AWS (ECS Fargate, S3, Lambda, Step Functions), Docker, Terraform, Git, React.
        \end{itemize}
        \vspace{-5pt}

        % Experience #2
        \resumeExperienceHeading{Teaching Assistant (OS \& Mobile App Development) \textbar\ \href{https://scai.engineering.asu.edu/}{SCAI, Arizona State University}}{Aug 2023 - Present}
        \begin{itemize}[itemsep=1pt]
            \item Raised lab pass rates from 62\% to 88\% as measured over 3 semesters, by mentoring 600+ students through targeted instruction in OS internals and SwiftUI, delivering 100+ hours of support, and maintaining a 4.5/5 avg. feedback rating.
            
            \item Reduced grading effort by 80\% and turnaround time by 3+ days by creating and deploying 5 core lab modules and auto-grading scripts using Bash scripting and Git-based pipelines.
            
            \item Improved project quality and cut setup/debugging time by 40\% by building SwiftUI starter templates used by 300+ students, standardizing architecture for consistent scaffolding and faster iteration.
            
            \item \textbf{Tech-stack:} C, C++, Swift, SwiftUI, Python, Linux, Bash, Xcode, Notion, Latex, Git.
        \end{itemize}
  \end{itemize}

\vspace{-15pt}
%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \begin{itemize}[itemsep=1pt,leftmargin=0in, label={}]
        % Project #1
        \resumeProjectHeading{Serverless REST API using AWS \textbar\ \href{https://github.com/YashShelar007/Serverless-Architecture}{GitHub}}{Jan 2024 - Apr 2024}
        \begin{itemize}[itemsep=1pt]
            \item Achieved scalable request handling (1,000+ req/sec) and reduced cold starts by building a fully serverless REST API with Cognito-based auth and DynamoDB workflows, optimizing cost and performance. 
            
            \item Reduced deployment time by 80\% by automating infrastructure provisioning via CloudFormation, ensuring consistent and reliable releases across staging and production environments
            
            \item \textbf{Tech-stack} AWS Lambda, API Gateway, DynamoDB, AWS Cognito, Python, CloudFormation.
        \end{itemize}

        % Project #2
        \resumeProjectHeading{Personalized AI-Driven Travel Planner \textbar\ \href{https://github.com/YashShelar007/VoyageAI}{GitHub}}{Mar 2024 - May 2024}
        \begin{itemize}[itemsep=1pt]
            \item Reduced travel planning time by 60\% by generating multi-day itineraries through Gemini AI, integrating real-time suggestions for flights, hotels, and activities using Google Places API.
            
            \item Scaled to 5,000+ concurrent sessions and improved session consistency by 35\% by integrating Firebase Auth, Firestore, and Expo Router for secure user flows and seamless multi-screen navigation. 
            
            \item \textbf{Tech-stack:} React Native, Gemini AI, Google Places API, Firebase, Expo.  
        \end{itemize}

        % Project #3
        \resumeProjectHeading{Full-Stack Ride-Sharing Mobile App \textbar\ \href{https://github.com/YashShelar007/ZipRide}{GitHub}}{Jan 2024 - Mar 2024}
        \begin{itemize}[itemsep=1pt]
            \item Enabled real-time ride booking and map navigation at scale by building a full-stack ride-sharing app load-tested to 10,000 concurrent sessions, supporting secure Stripe payments and user authentication with Clerk. 
            
            \item Reduced state inconsistency issues by 45\% by integrating Zustand for optimized local state handling and Stripe webhooks to track live checkout events and ride status updates. 
            
            \item \textbf{Tech-stack:} React Native, Neon PostgreSQL, Stripe, Clerk, Expo.
        \end{itemize}
    \end{itemize}

\end{document}